---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(simuCCP)
library(mvtnorm)
```

## Simulation 

We can use `simuCCP::simuCCP` to simulate data with pre-defined C-index and time dependent AUC.  

* `metrics` define different preditive metrics 
* `family`  define the copula family

### Single Marker

For a Gaussian copula (`family = 1`), we can simulate a dataset for C-index = 0.7.   

```{r}
db1 <- simuCCP(N = 200, metric = "Cind", value = 0.7, family = 1)
head(db1$data)
```

### Two Markers
For two markers with Gaussian and Clayton copulas (`family = c(1,3)`), we can simulate data for C-index both equal to 0.7. The conditional copula between two markers is Gumbel (`fam2 = 4`) with parameter 1 (`par2 = 1`)

```{r}
db2 <- simuCCP(300, metric = "Cind", value = 0.7, family = c(1,3), fam2 = 4, par2 = 1)
head(db2$data)
```

### Define parameters and predictive metrics

There are a set of functions to calculate parameter to predictive metric and vice versa. 

* C-index: `simuCCP::BiCopCind2Par` and `simuCCP::BiCopPar2Cind`  
* AUC: `simuCCP::BiCopAUC2Par` and `simuCCP::BiCopPar2AUC`

For example, we can find a clayton copula parameter for C-index equal to 0.75.

```{r}
simuCCP::BiCopCind2Par(family = 3, Cind = 0.75)
```



